### 2020-11-03 treatise/3_1_almost_sparsity.tex
Update discussion on numerical experiments
New figures for time taken

\startsection [title={Angular Channel Response is Almost-Sparse}]

\startsubsection [title={Norm of Array Response}]

Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity index \m {S} be fixed.
Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\MS {A}}}}, the largest \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\MS {B}}}} the next \m {s} largest components of \m {\V {g}}, and \m {\V {g} _{\SB{\MS {C}}}} are the components complement to \m {\V {g} _{\SB{\MS {A}}}}.
For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\MS {A}}} =\IP {0,3,0,0,8}}, \m {\V {g} _{\SB{\MS {B}}} =\IP {-1,0,0,2,0}}, and \m {\V {g} _{\SB{\MS {C}}} =\IP {-1,0,-4,2,0}}.
In this section, the subscripts \m {\MS {A}, \MS {B}, \MS {C}} will keep bearing analogous meaning.

We hope that \m {\VNm {\V {g} _{\SB{\MS {C}}}} _1} is small.
If so, we shall substitute the quantity into the expected square error of DS, thus generalizing to the almost-sparse case.
Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
We define, similarly, \m {\V {a} _{\SB{\MS {A}}}} and \m {\V {a} _{\SB{\MS {C}}}}, with sparsity \m {s}, different from \m {S}.
If \m {N_H} is large, we may forget for a moment the requirement that \m {s =1,2,3,\dots}.

First, we investigate
%
\DispNum {a:2:Ka:22} {
\NC \VNm {\V {a} \SB {\f} _{\SB{\MS {C}}}} _2 ^2
=\NC \VNm {\RB {\M {K}^\Adj \V {a} \SB {\f}} _{\SB{\MS {C}}}} _2 ^2 \NR
}
%
Let \m {\f} be fixed.
Towards that end, introduce
%
\DispNum {y':H:f'M:p'p'} {
\NC \psi \SB {\f, n_H}
:=\NC \RB {
   \f \; \Rm {Mod}\; \F {2\pi} {N_H}
   + \RB {\F {2 n_H} {N_H} + 1} \pi
} \;
\Rm {Mod}\; \RB {2\pi}
- \pi \NR
}
%
Note that by construction
%
\DispNum {y':H:p'::p':} {
\NC \Nm {\psi \SB {\f, n_H}}
\leq \NC \pi \NR
}
%
And define the so-called Dirichlet kernel
%
\DispNum {D:y':nH:Hy'} {
\NC D \SB {\psi'}
:= \NC \sum_{n_H=0}^{N_H-1} \Ss {e}^{i n_H \psi'} \NR
}
%
Set for short
%
\DispNum {b:f':Ka:af'} {
\NC b \SB {\f}
=\NC \M {K}^\Adj \V {a} \SB {\f} \NR
}
%
Then observe
%
\DispNum {K:H:1N:nH} {
\NC \RB {\V {b} \SB {\f}} _{\SB {n_H}}
=\NC \F {1} {N_H} D \SB {\psi \SB {\f, n_H}} \NR
}

Now, by the nature of alternating series, for \m {- \pi \leq x < \pi}, it holds that
%
\DispNum {x:6:si:nx} {
\NC \Nm {x - \F {x^3} {6}}
\leq \NC \Nm {\sin x}. \NR
}
Therefore,
%
\DispNum {D:y':si:y'p'} {
\NC \Nm {D \SB {\psi'}}
= \NC \F {\Nm {\sin \SB {N_H \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \NR
%
\NC \leq \NC B \SB {\psi'} \NR
%
\NC := \NC \F {48} {\Nm {\psi'^2 -24} \Nm {\psi'}} \NR
%
\NC - \pi \leq \NC \psi' < \pi. \NR
}
%
Combining \Rf {y':H:f'M:p'p'}, \Rf {K:H:1N:nH}, and \Rf {D:y':si:y'p'} we have
%
\DispNum {b:1:1N:C1} {
\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
=\NC \F {1} {N_H}
\VNm {
\RB {
   \sum_{n_H' =0}^{N_H -1}
      B \SB {\psi \SB {\f, n_H'}}
      \V {u} _{n_H'}
} _{\SB{\MS {C}}}
} _1
\NR
}
%
Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
We seek to bound the \quotation {rectangulars} with an integral, and we have to split the cases that \m {N_H} is odd and even.
Anyway, a moment's reflection shows
%
\DispNum {b:1:1N:NH} {
\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
\leq \NC \F {1} {N_H} \D \F {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
%
\NC = \NC \F {48} {N_H \pi^3}
\int _{s /N_H} ^1 \F {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \NR
%
\NC =\NC \F {1} {\pi} \log \F {N_H^2 /s^2 - \pi^2 /24} {1 - \pi^2 /24} \NR
%
\NC \eqsim \NC \F {2} {\pi} \RB {\log N_H - \log s} \NR
%
\NC \leq \NC \F {2} {\pi} \log N_H \NR
}
%
Since the value of \m {s} is at our disposal, we try
%
\DispNum {s:s:lo:NH} {
\NC s
=\NC \R {\log N_H} \NR
}
%
so that, by \m {\ell_p}-norm inequality,

\Result
{Proposition}
{
Let \m {\f } be given, and linear array response in spacial frequency domain \m {\V {b} \SB {\f}} defined in \Rf {b:f':Ka:af'}.
Then, for any random instance of \m {\f},
%
\DispNum {a:2:4N:NH} {
\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _2
\leq \NC \F {2} {\pi} \log N_H \NR
}
}

@@

\startsubsection [title={Norm of Angular Channel Response}]

If we set that
\DispNum {S:S:Ls:s2} {
\NC S
=\NC L s^2 \NR
}
by triangle inequality, by the property of 2-norm and Frobenius norm,
%
\DispNum {g:1:l0:a'1} {
\NC \VNm {\V {g} _{\SB{\MS {C}}}} _1
\leq \NC
\sum _{l=0} ^{L-1} \Nm {\a_l}
\VNm {\V {b} \SB {\f_l} _{\SB{\MS {C}}}} _2
\VNm {\V {b} \SB {\th_l} _{\SB{\MS {C}}}} _2 \NR
%
\NC \leq \NC
\VNm {\V {b} \SB {\f_l} _{\SB{\MS {C}}}} _2
\VNm {\V {b} \SB {\th_l} _{\SB{\MS {C}}}} _2
\sum _{l=0} ^{L-1} \Nm {\a_l} \NR
%
\NC \leq \NC
\F {4} {\pi^2} L \RB {\log N_H}^2 \D
\F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
}
%
The quantity
\DispNum {1:l:::} {
\NC \NC \F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
}
is a sample mean, and we may want to use Hoeffding inequality.
Since it requires that the random variable shall have compact support, we truncate \m {\Nm {\a_l}} on \m {\Nm {\a_l} \leq 2}, on which there is 95 percent of the probability mass.
%
To do so, observe that
%
\DispNum {E:1:2p':2p'} {
\NC \MB {E} \SB {\F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}}
=\NC \F{\R {2}} {\R {\pi}} \NR
}
So, by Hoeffding inequality, choose for simplicity
%
\DispNum {P:p':2e:3p'} {
\NC \MB {P} \SB {
   \F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}
   \geq \F {4 \R{2}} {\R {\pi}}
}
\leq \NC 2 \exp \SB {- \F {9L} {\pi}} \NR
}
%
Now we have
\DispNum {g:2:12:43} {
\NC \F {\VNm {\M {g} _{\SB{\MS {C}}}} _1} {\RB {\log N_H}^2}
\leq \NC \F {12 \R{2}} {\pi ^{5/2}}
\leq 4/3. \NR
}
%
\Result
{Proposition}
{
et \m {\V {g} \in \MB {C} ^{N_H^2}} be defined as in \Rf {g:g:ve:Nh}.
Then the bound
%
\DispNum {g:C:4p':NH} {
\NC \VNm {\M {g} _{\SB{\MS {C}}}} _1
\leq \NC \F {4} {3} \RB {\log N_H}^2 \NR
}
%
holds for probability \m {p}, with
%
\DispNum {1:p:1N:H3} {
\NC 1 -p
\leq \NC 2 \exp \SB {- \F {9L} {\pi}} \NR
}
}

>>>>

\startsection [title={Angular channel response is almost-sparse}]

\startsubsection [title={Norm of array response}]

Let \m {\hat {\V {g}}} be the Dantzig Selector, and let the sparsity level \m {S} be fixed.
Split \m {\V {g}} into two parts: \m {\V {g} _{\SB{\MS {A}}}}, the largest-magnitude \m {s} components of \m {\V {g}}, \m {\V {g} _{\SB{\MS {B}}}} the next \m {s} largest-magnitude components of \m {\V {g}}, and \m {\V {g} _{\SB{\MS {C}}}} are the components complement to \m {\V {g} _{\SB{\MS {A}}}}.
For example, if \m {\V {g} =\IP {-1,3,-4,2,8}}, and \m {S=2}, then \m {\V {g} _{\SB{\MS {A}}} =\IP {0,0,-4,0,8}}, \m {\V {g} _{\SB{\MS {B}}} =\IP {0,3,0,2,0}}, and \m {\V {g} _{\SB{\MS {C}}} =\IP {-1,3,0,2,0}}.
In this section, the subscripts \m {\MS {A}, \MS {B}, \MS {C}} will bear analogous meaning.

We hope that \m {\VNm {\V {g} _{\SB{\MS {C}}}} _1} is small.
If so, we shall substitute the quantity into the expected square error of DS, thus generalizing to the almost-sparse case.
Recall that \m {\M {G}} is just the vectorization of \m {\V {g}}, and is the function of \m {\V {a}}, so we seek to establish that \m {\V {a}} is almost sparse.
We define, similarly, \m {\V {a} _{\SB{\MS {A}}}} and \m {\V {a} _{\SB{\MS {C}}}}, with sparsity level \m {s} different from \m {S}.
If \m {N_H} is large, we may forget for a moment that \m {s} is an integer.

First, we investigate
%
\DispNum {a:2:Ka:22} {
\NC \VNm {\V {a} \SB {\f} _{\SB{\MS {C}}}} _2 ^2
=\NC \VNm {\RB {\M {K}^\Adj \V {a} \SB {\f}} _{\SB{\MS {C}}}} _2 ^2 \NR
}
%
Let \m {\f} be fixed.
Towards that end, introduce
%
\DispNum {y':H:f'M:p'p'} {
\NC \psi \SB {\f, n_H}
:=\NC \RB {
   \f \; \Rm {Mod}\; \F {2\pi} {N_H}
   + \RB {\F {2 n_H} {N_H} + 1} \pi
} \;
\Rm {Mod}\; \RB {2\pi}
- \pi \NR
}
%
Note that by construction
%
\DispNum {y':H:p'::p':} {
\NC \Nm {\psi \SB {\f, n_H}}
\leq \NC \pi \NR
}
%
And set for short
%
\DispNum {D:y':nH:Hy'} {
\NC D \SB {\psi'}
:= \NC \sum_{n_H=0}^{N_H-1} \Ss {e}^{i n_H \psi'} \NR
}
%
And
%
\DispNum {b:f':Ka:af'} {
\NC \V {b} \SB {\f}
=\NC \M {K}^\Adj \V {a} \SB {\f} \NR
}
%
Then observe
%
\DispNum {K:H:1N:nH} {
\NC \RB {\V {b} \SB {\f}} _{\SB {n_H}}
=\NC \F {1} {N_H} D \SB {\psi \SB {\f, n_H}} \NR
}

Now, by the nature of alternating series, for \m {- \pi \leq x < \pi}, it holds that
%
\DispNum {x:6:si:nx} {
\NC \Nm {x - \F {x^3} {6}}
\leq \NC \Nm {\sin x}. \NR
}
Therefore,
%
\DispNum {D:y':si:y'p'} {
\NC \Nm {D \SB {\psi'}}
= \NC \F {\Nm {\sin \SB {N_H \psi'/2}}} {\Nm {\sin \SB {\psi' /2}}} \NR
%
\NC \leq \NC B \SB {\psi'} \NR
%
\NC := \NC \F {48} {\Nm {\psi'^2 -24} \Nm {\psi'}} \NR
%
\NC - \pi \leq \NC \psi' < \pi. \NR
}
%
Combining \Rf {y':H:f'M:p'p'}, \Rf {K:H:1N:nH}, and \Rf {D:y':si:y'p'} we have
%
\DispNum {b:1:1N:C1} {
\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
\leq \NC \F {1} {N_H}
\VNm {
\RB {
   \sum_{n_H' =0}^{N_H -1}
      B \SB {\psi \SB {\f, n_H'}}
      \V {u} _{n_H'}
} _{\SB{\MS {C}}}
} _1
\NR
}
%
Note that \m {\Nm {B \SB {\psi'}}} is strictly decreasing in \m {\SB {0,\pi}}.
We seek to bound the \quotation {rectangulars} with an integral, and we have to split the cases that \m {N_H} is odd and even.
Anyway, a moment's reflection shows
%
\DispNum {b:1:1N:NH} {
\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
\leq \NC \F {1} {N_H} \D \F {N_H} {2\pi} \D 2 \int_{\pi s/N_H}^{\pi} B \SB {\psi'} ^2 d \psi' \NR
%
\NC = \NC \F {48} {N_H \pi^3}
\int _{s /N_H} ^1 \F {1} {\RB {24/\pi^2 -x'^2} ^2 x'^2} dx' \NR
%
\NC =\NC \F {1} {\pi} \log \F {N_H^2 /s^2 - \pi^2 /24} {1 - \pi^2 /24} \NR
%
\NC \eqsim \NC \F {2} {\pi} \RB {\log N_H - \log s} \NR
%
\NC \leq \NC \F {2} {\pi} \log N_H \NR
}
%
Since the value of \m {s} is at our disposal, we try
%
\DispNum {s:s:lo:NH} {
\NC s
=\NC \R {\log N_H} \NR
}
%
so that, by \m {\ell_p}-norm inequality, we have the following estimation.

\Result
{Proposition}
{
Let \m {\f } be given, and linear array response in spacial frequency domain \m {\V {b} \SB {\f}} defined in \Rf {b:f':Ka:af'}.
Then, for any random instance of \m {\f},
%
\DispNum {a:2:4N:NH} {
\NC \VNm {\V {b} \SB {\f} _{\SB{\MS {C}}}} _1
\leq \NC \F {2} {\pi} \log N_H \NR
}
}

@@

\startsubsection [title={Norm of angular channel response}]

If we set that
\DispNum {S:S:Ls:s2} {
\NC S
=\NC L s^2 \NR
}
by triangle inequality, by the property of Frobenius norm,
%
\DispNum {g:1:l0:a'1} {
\NC \VNm {\V {g} _{\SB{\MS {C}}}} _1
\leq \NC
\sum _{l=0} ^{L-1} \Nm {\a_l}
\VNm {\V {b} \SB {\f_l} _{\SB{\MS {C}}}} _1
\VNm {\V {b} \SB {\th_l} _{\SB{\MS {C}}}} _1 \NR
%
\NC \leq \NC
\VNm {\V {b} \SB {\f_l} _{\SB{\MS {C}}}} _1
\VNm {\V {b} \SB {\th_l} _{\SB{\MS {C}}}} _1
\sum _{l=0} ^{L-1} \Nm {\a_l} \NR
%
\NC \leq \NC
\F {4} {\pi^2} L \RB {\log N_H}^2 \D
\F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
}
%
The quantity
\DispNum {1:l:::} {
\NC \NC \F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l} \NR
}
is a sample mean, and we may want to use Hoeffding inequality.
Since it requires that the r.v.\ shall have compact support, we truncate \m {\Nm {\a_l}} on \m {\Nm {\a_l} \leq 2} for simplicity, on which there is 95 percent of the probability mass.
%
To do so, observe that
%
\DispNum {E:1:2p':2p'} {
\NC \MB {E} \SB {\F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}}
=\NC \F{\R {2}} {\R {\pi}} \NR
}
So, by Hoeffding inequality, choose also for simplicity
%
\DispNum {P:p':2e:3p'} {
\NC \MB {P} \SB {
   \F {1} {L} \sum _{l=0} ^{L-1} \Nm {\a_l}
   \geq \F {4 \R{2}} {\R {\pi}}
}
\leq \NC 2 \exp \SB {- \F {9L} {\pi}} \NR
}
%
Now we have
\DispNum {g:2:12:43} {
\NC \F {\VNm {\M {g} _{\SB{\MS {C}}}} _1} {\RB {\log N_H}^2}
\leq \NC \F {12 \R{2}} {\pi ^{5/2}}
\leq \F {4} {3}. \NR
}
%
\Result
{Proposition}
{
et \m {\V {g} \in \MB {C} ^{N_H^2}} be defined as in \Rf {g:g:ve:Nh}.
Then the bound
%
\DispNum {g:C:4p':NH} {
\NC \VNm {\M {g} _{\SB{\MS {C}}}} _1
\leq \NC \F {4} {3} \RB {\log N_H}^2 \NR
}
%
holds for probability \m {p}, with
%
\DispNum {1:p:1N:H3} {
\NC 1 -p
\leq \NC 2 \exp \SB {- \F {9L} {\pi}} \NR
}
}

### 2020-11-03 treatise/3_2_confirming_restricted_isometry.tex
New figures for time taken

\startsubsection [title={Design of beamformer matrices}]

Our plan is setting the four precoder matrices to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.

Let us make it simple and set each entry of \m {\M {F} _B} to be i.i.d.\ Normal r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
We know that the magnitude \m {\RB {\M {F} _B} _{\SB {n_R, n_Y}}} follows Rayleigh distribution.
\m {\RB {\M {W} _B ^\Tr} _{\SB {n_Y, n_R}}} is set in an entirely analolous manner.

In addition, let \m {\RB {\M {F} _R} _{\SB {n_H, n_R}}} be uniformly distributed on the unit circle on the complex plane.
\m {\RB {\M {W} _R ^\Tr} _{\SB {n_Y, n_R}}} is set in an entirely analolous manner.

@@

However, it is not clear that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr}, the product of two RIP matrices, have RIP, nor that, \m {\M {P}}, the result of Kronecker product, is RIP.
In fact, the statement seems to be false in general.
Indeed, since a \m {\M {F} _R ^\Tr} of the same \m {\d} is sparse, up to a factor of isometry matrix, and \m {\M {F} _R ^\Tr} is generated randomly, it would seem to us that the probability that \m {\M {F} _R ^\Tr \V {u}} be sparse is exceedingly small.

But all is not lost.
At least we have made sure that \m {\M {F} _R ^\Tr \V {u}} has norm close to unity.
If we have a stronger result, that \m {\M {F} _B ^\Tr \V {u}} is almost unitary even for \It {not-sparse} vectors, then we are done.
That does sound somehow plausible, considering the Normal entries of \m {\M {F} _B ^\Tr} would introduce a Central-limit-theorem-like sum, though the summands are not independent, but weakly dependent.

@@

To start, use \m {\chi _{i,j}} to denote Complex Standard Normal random variables, and to simplify notation, let them be independent if they have different arguments.
With this,
%
\DispNum {C':C':WB:j2} {
\NC \VNm {\M {W} _B \V {u}} _2
=\NC \R {
   \sum _{i=0} ^{N_B-1} \VNm {\sum _{j=0} ^{N_R-1} \F {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} \NR
}
%
Essentially, we seek for a large- deviation result for i.i.d.\ sum of chi-square random variables now.
To so so, we may apply Lemma 1 in Laurent and Massart \cite [LaM00] for equal weights.
By some calculation, we have upper tail inequality, for \m {x > 0},
%
\DispNum {P:x:ex:ex} {
\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\F {x} {N_B}} + \F {2x} {N_B}}
\leq \NC \Ss {e} ^{-x} \NR
}
%
And lower tail inequality
%
\DispNum {P:x:ex:ex!} {
\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 + 2 \R {\F {x} {N_B}}}
\leq \NC \Ss {e} ^{-x} \NR
}
%
With substitution \m {\d_s =16x^2 /N_B^2}, the upper tail can be simplified with \m {x <N_B}, and we get the following bound for failure probability.

@@

Here, we consult Haviv and Regev, ``The restricted isometry property of subsampled Fourier matrices'' collected in \cite [KlM17].
We need their Thm.\ 4.5; it gives a RIP guarantee w.r.t.\ \m {\d_s}, and probability lower bound, for DFT submatrix.
The estimation they give involve is expressed in terms of big- \m {\O} and big- \m {O}, and since our methodology is 
However, it can be seen that their argument allows precise constants, and they just did not spell out, which we briefly explain.
Roughly, they use Chernoff-Hoeffding bounds, but write the exponent in the form of \m {\Omega}.
Starting in their Thm.\ 2.2, we may substitute (say) \m {C \leftarrow 1/3} in place of their big- \m {\Omega}.
The conclusions, their Thm.\ 3.7 and Thm.\ 4.5, may be changed accordingly.
If modified with respect to our setting, the condition
%
\DispNum {N:R:sd':NH} {
\NC N_R
\geq \NC \F {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \NR
}
%
guarantees a failure probability \m {\d_s /N_H s}.
We would like to drop \m {\log \SB {1 /\d_s}^2} and the denominator \m {\d_s} in \m {\log \SB {s /\d_s}^2} in \Rf {N:R:sd':NH}.

>>>>

\startsubsection [title={Design of beamformers}]

Our plan is setting the four beamformers to be i.i.d.\ random matrix, hoping that the resulting \m {P} has RIP.
Let us make it simple and set each entry of \m {\M {F} _B} to be i.i.d.\ normal r.v.\ with mean 0, standard deviation \m {1/2}, multiplied by a normalizing constant \m {\l_B >0}.
We know that the magnitude \m {\RB {\M {F} _B} _{\SB {n_R, n_Y}}} follows Rayleigh distribution.
\m {\RB {\M {W} _B ^\Tr} _{\SB {n_Y, n_R}}} is set in an entirely analolous manner.
In addition, let \m {\RB {\M {F} _R} _{\SB {n_H, n_R}}} be uniformly distributed on the unit circle on the complex plane.
\m {\RB {\M {W} _R ^\Tr} _{\SB {n_Y, n_R}}} is set in an entirely analolous manner.

@@

However, it is not clear that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr}, the product of two RIP matrices, have RIP, nor that, \m {\M {P}}, the result of Kronecker product, is RIP.
In fact, the statement seems to be false in general.
But all is not lost.
Can we argue instead that \m {\M {F} _B ^\Tr \M {F} _R ^\Tr \V {u}} has similar norm with \m {\M {F} _R ^\Tr \V {u}}?

@@

Use \m {\chi _{i,j}} to denote complex standard normal r.vs., and to simplify notation, let them be independent if they have different indices.
With this,
%
\DispNum {C':C':WB:j2} {
\NC \VNm {\M {W} _B \V {u}} _2
=\NC \R {
   \sum _{i=0} ^{N_B-1} \VNm {\sum _{j=0} ^{N_R-1} \F {1} {\R{N_B}} \chi _{i,j} \V {u} _{j}} _2 ^2} \NR
}
%
Essentially, we seek for a large- deviation result for i.i.d.\ sum of chi-square r.vs.\ now.
To so so, we may apply Lemma 1 in Laurent and Massart \cite [LaM00] for equal weights.
By some calculation, we have upper tail inequality, for \m {x > 0},
%
\DispNum {P:x:ex:ex} {
\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \geq 1 + 2 \R {\F {x} {N_B}} + \F {2x} {N_B}}
\leq \NC \Ss {e} ^{-x} \NR
}
%
And lower tail inequality
%
\DispNum {P:x:ex:ex!} {
\NC \MB {P} \SB {\VNm {\M {W} _B \V {u}} _2 ^2 \leq 1 - 2 \R {\F {x} {N_B}}}
\leq \NC \Ss {e} ^{-x} \NR
}
%
With substitution \m {\d_s =16x^2 /N_B^2}, the upper tail can be simplified with \m {x <N_B}, and we get the following bound for failure probability.

@@

Here, we consult Haviv and Regev, “The restricted isometry property of subsampled Fourier matrices” collected in \cite [KlM17].
We need their Thm.\ 4.5; it gives a RIP guarantee w.r.t.\ \m {\d_s}, and probability lower bound, for DFT submatrix.
The estimation they give involve is expressed in terms of big- \m {\O} and big- \m {O}, and since our methodology is 
However, it can be seen that their argument allows precise constants, and they just did not spell out, which we briefly explain.
Roughly, they use Chernoff-Hoeffding bounds, but write the exponent in the form of \m {\Omega}.
Starting in their Thm.\ 2.2, we may substitute (say) \m {C \leftarrow 1/3} in place of their big- \m {\Omega}.
The conclusions, their Thm.\ 3.7 and Thm.\ 4.5, may be changed accordingly.
If modified with respect to our setting, the condition
%
\DispNum {N:R:sd':NH} {
\NC N_R
\geq \NC \F {s} {\d_s^2} \RB {\log \F{1}{\d_s}}^2 \RB {\log \F{s}{\d_s}}^2 \log N_H \NR
}
%
guarantees a failure probability \m {\d_s /N_H s}.
We would like to drop \m {\log \SB {1 /\d_s}^2} and the denominator \m {\d_s} in \m {\log \SB {s /\d_s}^2} in \Rf {N:R:sd':NH}.
